Android security updates

### 2014-02-11 QInF.tex
QInF: Update text with comments from Alastair

The Internet of Things means that there will be many more internet connected devices, these will have software / firmware running on them.
Security vulnerabilities will be found in this software and firmware which will then need to be updated.
Android is one operating system which is being used for various Internet of Things devices (fridges, toasters etc.) and so examining the trends in security updates for Android gives us insight into how updates for Internet of Things devices might evolve.
Our preliminary results indicate that most Android devices do not receive security updates in a timely manner.
I intend to quantify this more precisely and compare different manufacturers to determine which are the best at shipping security updates promptly.
Initial analysis indicates that perhaps the Qualcomm Innovation Center, Inc. (QuIC) is the best at following best practice\footnote{\url{https://www.codeaurora.org/projects/security-advisories}} and Google the best at shipping updates to devices promptly.

\section*{Innovation proposal and relation to the state of the art}
Presently there is not much visibility into the impact of security vulnerabilities on Android, many root equivalent vulnerabilities do not even have CVEs registered even when they are being actively exploited.
It is also difficult to determine when vulnerabilities have been fixed and these fixes propagated to users.
I have produced the Android Vulnerabilities website\footnote{\url{http://androidvulnerabilities.org/}} to collate this information.
By using the database of root equivalent vulnerabilities that I have collected and the Device Analyzer\footnote{\url{https://deviceanalyzer.cl.cam.ac.uk/}}~\cite{TODO} data we can determine the proportion of devices running vulnerable versions of Android.
We can then chart how that changes over time as new vulnerabilities are discovered and old ones are fixed, this is shown in Figure \ref{fig:propinsecure}.

@@

There is still much to do to tie down details and give a more representative coverage of root equivalent vulnerabilities on Android.
In particular manufacturer specific flaws are under-represented and there are many details which need to be tracked down to improve the accuracy of the results.

>>>>

The Internet of Things means that there will be many more internet connected devices, these will have software / firmware running on them.
Security vulnerabilities will be found in this software and firmware which will then need to be updated.
Android is one operating system which is being used for various Internet of Things devices (fridges, toasters etc.) and so examining the trends in security updates for Android gives us insight into how updates for Internet of Things devices might evolve.
Our preliminary results indicate that most Android devices do not receive security updates in a timely manner.
Android devices are user facing and probably more likely to receive updates than fridges or water meters so the situation is likely to be worse.
I intend to quantify this more precisely and compare different manufacturers to determine which are the best at shipping security updates promptly.
Initial analysis indicates that perhaps the Qualcomm Innovation Center, Inc. (QuIC) is the best at following best practice\footnote{\url{https://www.codeaurora.org/projects/security-advisories}} and Google the best at shipping updates to devices promptly.

\section*{Innovation proposal and relation to the state of the art}
Presently there is not much visibility into the impact of security vulnerabilities on Android, many root equivalent vulnerabilities do not even have CVEs registered even when they are being actively exploited.
It is also difficult to determine when vulnerabilities have been fixed and these fixes propagated to users.
I have produced the Android Vulnerabilities website\footnote{\url{http://androidvulnerabilities.org/}} to collate this information.
Root equivalent vulnerabilities are vulnerabilities which can be exploited either to gain root or to gain privileges which can then be used to gain root on the device.
By using the database of root equivalent vulnerabilities that I have collected and the Device Analyzer\footnote{\url{https://deviceanalyzer.cl.cam.ac.uk/}}~\cite{TODO} data we can determine the proportion of devices running vulnerable versions of Android.
We can then chart how that changes over time as new vulnerabilities are discovered and old ones are fixed, this is shown in Figure \ref{fig:propinsecure}.

@@

There is still much to do, we have only just started.
We need a more representative coverage of root equivalent vulnerabilities on Android, currently we only have a subset with many important details missing from the ones which we have.
In particular manufacturer specific flaws are under-represented and there are many details which need to be tracked down to improve the accuracy of the results.
There is also information which is not presently publicly available but which it might be possible to ask manufacturers and those who found vulnerabilities for in order to get a better picture of what is actually happening.
Presently while we can chart the data we have, we cannot be sure that it is representative.
